TGI Spinal Analysis Code

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
merging dmographics

# Data organisation
```{r}
# recode conditions
df_res <- df_res %>%
  mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
         cold_probe = recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
                             'dist' = 'distal', 'prox' = 'proximal'))
# change levels 
df_res$cold_probe <- factor(df_res$cold_probe, 
                            levels = c("caudal", "rostral", "distal", "proximal"))

@@

# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
# then plot :D
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")

ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
  geom_point(position = position_dodge(.2)) +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(grey[3], blue[4])) +
  theme_bw()
```

>>>>

# Data organisation
```{r}
# transform the ID of participants to remove 0

# recode conditions
df_res <- df_res %>%
  mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
         cold_probe = recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
                             'dist' = 'distal', 'prox' = 'proximal'))
# change levels 
df_res$cold_probe <- factor(df_res$cold_probe, 
                            levels = c("caudal", "rostral", "distal", "proximal"))

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
test <- merge(df_res, df_demo)

@@

# plot distribution of data
ggplot(df_long) +
  geom_density(aes(VAS, colour = manipulation)) +
  facet_wrap(~quality, scales = "free_y") +
  theme_bw()
```
# MAIN HYPOTHESES
# Plot descriptives for each hypotheses
Hypothesis 1: within vs. across dermatomes

```{r}
# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
                      median, data = all_vas)
vas_h1 <- aggregate(VAS)
# then plot :D
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")

ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
  geom_point(position = position_dodge(.2)) +
  facet_grid(~quality*manipulation) +
  scale_colour_manual(values = c(grey[3], blue[4])) +
  theme_bw()
```

Hypothesis 2 a & b: relative location of warm and cold
